\feedbacktitle{Summer Geometry Institute}{2021, 2023}{During the summers of 2021 and 2023 (the latter together with my colleague Ana Dodik), I worked as a mentor for MIT's Summer Geometry Intiative, founded by Professor Justin Solomon. In it, I directed two projects for two groups of undergraduate students from underrepresented communities new to geometry processing. Below is a representative sample of the anonymous feedback collected by Prof. Solomon}
\feedbackitem{Ana and Silvia built a collaborative, safe, open environment for new ideas. Both taught us a lot about how to research and approach problems with different approaches. They are outstanding researchers that I admire even more now.}
\feedbackitem{Ana and Silvia are both absolutely fantastic mentors!}
\feedbackitem{This week has been great! Ana and Silvia are excellent mentors. They created an excellent environment for us to learn and collaborate}
\feedbackitem{I still have no idea what Silvia's role was, but she went above and beyond to help out with everything. She made us all feel welcome in the Slack channel before SGI even started and continued to dole out advice and support throughout the whole of SGI. She also patiently answered my millions of questions almost as quickly as I could ask them.}
\feedbackitem{Silvia ensured we all felt welcome right from the beginning of the Slack channel. When we introduced ourselves, I noticed she found something nice to say to each of us, and it felt very welcoming to have that display of friendliness right from the get-go.}
\feedbackitem{Silvia Sellán, I would like to thank you specifically for the SGP \& Siggraph 2021 WiGraph event, sharing your thoughts in grad school event and being accessible.}
