\talktitle{Uncertainty Quantification in 3D Geometric Synthesis}
\talkvenue{University of Zaragoza Graphics and Imaging seminar}{hosted by Prof. Ana Serrano}{Virtual}{November 2023}
\talkvenue{Brown University Graphics seminar}{hosted by Prof. Daniel Ritchie}{Virtual}{October 2023}
\talkvenue{Banff International Research Station 3D Generative Modeling Workshop}{Invited talk}{Banff (Canada)}{July 2023}
\talktitle{Geometry +: Uncertain Surface Reconstruction}
\talkvenue{École polytechnique Graphics seminar}{hosted by Prof. Maks Ovsjanikov}{Paris (France)}{July 2023}
\talkvenue{INRIA seminar}{hosted by Profs. Bruno Lévy and Sylvain Lefebvre}{Nancy (France)}{June 2023}
\talkvenue{CNRS seminar}{hosted by Dr. Julie Digne}{Lyon (France)}{June 2023}
\talkvenue{University of Navarra Graphics and Vision seminar}{hosted by Prof. Asier Marzo}{Pamplona (Navarra)}{June 2023}
\talkvenue{University of Edinburgh Geometry seminar}{hosted by Prof. Amir Vaxman}{Edinburgh (Scotland)}{June 2023}
\talkvenue{Adobe Research seminar}{hosted by Dr. Valentin Deschaintre}{London (England)}{June 2023}
\talkvenue{University College London Vision seminar}{hosted by Prof. Kaan Akşit}{London (England)}{June 2023}
\talkvenue{University of British Columbia Graphics seminar}{hosted by Prof. Alla Sheffer}{Vancouver (Canada)}{June 2023}
\talkvenue{Simon Fraser University Vision seminar}{hosted by Prof. Andrea Tagliasacchi}{Vancouver (Canada)}{June 2023}
\talkvenue{EPFL Graphics seminar}{hosted by Prof. Mark Pauly}{Lausanne (Switzerland)}{May 2023}
\talkvenue{ETH Graphics seminar}{hosted by Prof. Olga Sorkine-Hornung}{Zürich (Switzerland)}{May 2023}
\talkvenue{University of Waterloo Graphics seminar}{hosted by Prof. Craig Kaplan}{Waterloo (Canada)}{April 2023}
\talkvenue{University of Montreal Graphics seminar}{hosted by Prof. Mikhail Bessmeltsev}{Montréal (Québec)}{November 2022}
\talkvenue{Johns Hopkins Graphics seminar}{hosted by Prof. Misha Kazhdan}{Baltimore (United States)}{November 2022}
\talkvenue{Columbia University Graphics seminar}{hosted by Prof. Changxi Zheng}{New York City (United States)}{November 2022}
\talkvenue{New York University Graphics seminar}{hosted by Prof. Daniele Panozzo}{New York City (United States)}{November 2022}
\talkvenue{MIT Graphics seminar}{hosted by Prof. Justin Solomon}{Cambridge (United States)}{November 2022}
\talkvenue{Dartmouth Graphics and Rendering seminar}{hosted by Prof. Wojciech Jarosz}{Hanover (United States)}{November 2022}
\talkvenue{TomatoGRAPH}{Technical Talk}{Toronto (Canada)}{December 2021}
\talktitle{Mesh Math and Beyond: An introduction to shape representations}
\talkvenue{Summer Geometry Initiative}{Full-day tutorial}{Virtual}{July 2023}
\talkvenue{Summer Geometry Initiative}{Full-day tutorial}{Virtual}{July 2022}
\talkvenue{Summer Geometry Initiative}{Full-day tutorial}{Virtual}{July 2021}
\talktitle{Blender for Academic Papers}
\talkvenue{Graphics Interface}{Invited Course}{Victoria (Canada)}{June 2023}
\talkvenue{Geometry and Architecture Summit}{Invited Talk}{Toronto (Canada)}{October 2022}
\talkvenue{ACM / Eurographics SGP}{Invited Course}{Virtual}{June 2022}
\talktitle{Geometry +: Moving Fast, Breaking Things and Putting Them Back Together}
\talkvenue{University of Southern California Graphics seminar}{hosted by Prof. Oded Stein}{Los Angeles (United States)}{April 2023}
\talkvenue{McGill University Graphics seminar}{hosted by Prof. Oded Stein}{Montréal (Québec)}{November 2022}
\talkvenue{Ubisoft research seminar}{hosted by the LaForge team}{Montréal (Québec)}{November 2022}
\talkvenue{Yale University Rising Stars seminar}{hosted by Prof. Theodore Kim}{New Haven (United States)}{November 2022}
\talkvenue{Engineering and Applied Science Forum}{hosted by the EASF team}{Virtual}{November 2022}
\talktitle{Uncertain Surface Reconstruction}
\talkvenue{UCLA and CalTech's Grundfest Memorial Lecture}{hosted by Profs. Achuta Kadambi and Katie Bouman}{Virtual}{March 2023}
\talktitle{Research in Geometry Processing}
\talkvenue{University of Toronto Undergraduate Graphics Club}{Invited Talk}{Toronto (Canada)}{February 2023}
\talktitle{Stochastic Poisson Surface Reconstruction}
\talkvenue{ACM SIGGRAPH Asia}{Technical Paper presentation}{Daegu (South Korea)}{December 2022}
\talktitle{Breaking Good: Fracture Modes for Realtime Destruction}
\talkvenue{ACM SIGGRAPH Asia}{Technical Paper presentation}{Daegu (South Korea)}{December 2022}
\talktitle{Breaking Bad: A Dataset for Geometric Fracture Reassembly}
\talkvenue{NeurIPS}{Featured (oral) paper presentation}{New Orleans (United States)}{November 2022}
\talktitle{Virtual Bodies that Matter: A Trans Researcher''s Career in Computer Graphics}
\talkvenue{Georgetown's Gender and Media Seminar}{hosted by Prof. Amanda Phillips}{Washington, D.C. (United States)}{November 2022}
\talktitle{Sex and Gender in the Computer Graphics Literature}
\talkvenue{Queer in AI @ NeurIPS workshop}{Invited Talk}{New Orleans (United States)}{November 2022}
\talkvenue{UNC Chapel Hill}{hosted by Prof. Roni Sengupta}{New Orleans (United States)}{November 2022}
\talkvenue{ACM SIGGRAPH}{Talk presentation}{Vancouver (Canada)}{August 2022}
\talktitle{A Deep Dive into Implicit Swept Volumes}
\talkvenue{University of Toronto Undergraduate Graphics Club}{Invited Talk}{Toronto (Canada)}{March 2022}
\talkvenue{INRIA MFX research seminar}{hosted by Prof. Sylvain Lefebvre}{Virtual}{June 2021}
\talkvenue{MIT Graphics research seminar}{hosted by Prof. Justin Solomon}{Virtual}{June 2021}
\talkvenue{GraphQUON}{Technical presentation}{Virtual}{December 2020}
\talktitle{Swept Volumes via Spacetime Numerical Continuation}
\talkvenue{ACM SIGGRAPH}{Technical Paper presentation}{Virtual (originally Los Angeles)}{August 2021}
\talktitle{An Introduction to GP Programming in MATLAB with Gptoolbox}
\talkvenue{ACM / Eurographics SGP}{Invited Course}{Virtual}{July 2021}
\talktitle{Developable Surfaces: A Case Study in Discrete Differential Geometry}
\talkvenue{Lancaster University Pure Mathematics Postgraduate Forum}{Invited Talk}{Virtual}{March 2021}
\talkvenue{Technion research seminar}{hosted by Prof. Mirela Ben-Chen}{Virtual}{December 2020}
\talkvenue{Carnegie Mellon University Geometry seminar}{hosted by Prof. Keenan Crane}{Virtual}{November 2020}
\talktitle{Seamless Integration of Virtual and Real World}
\talkvenue{Eurographics 2021}{Doctoral Consortium talk}{Virtual (originally Vienna)}{May 2021}
\talkvenue{University of Toronto}{PhD Qualifying Exam}{Toronto (Canada)}{September 2020}
\talktitle{Opening and Closing Surfaces}
\talkvenue{ACM SIGGRAPH Asia}{Technical Paper presentation}{Virtual (originally Daegu)}{December 2020}
\talkvenue{Epic Games}{hosted by Dr. Ryan Schmidt}{Virtual}{November 2020}
\talkvenue{Fields Institute Undergraduate Summer Research Program}{End-of-summer research talk}{Toronto (Canada)}{August 2017}
\talkvenue{University of Toronto DCS Summer Research Program}{Mid-summer research talk}{Toronto (Canada)}{July 2017}
\talktitle{Developability of Heightfields via Rank Minimization}
\talkvenue{Toronto Geometry Colloquium}{Opener talk for Prof. Olga Sorkine-Hornung}{Virtual}{October 2020}
\talkvenue{SIGGRAPH 2020}{Technical Paper presentation}{Virtual (originally Washington, D.C.)}{August 2020}
\talktitle{Solid Geometry Processing on Deconstructed Domains}
\talkvenue{Stanford University Graphics seminar}{hosted by Prof. Doug James}{Stanford (United States)}{October 2019}
\talkvenue{ACM / Eurographics SGP}{Technical Paper presentation}{Milan (Italy)}{July 2019}
\talkvenue{Toronto-Montreal Area Graphics workshop}{Technical talk}{Toronto (Canada)}{December 2017}
\talkvenue{Fields Institute Undergraduate Summer Research Program}{End-of-summer research talk}{Toronto (Canada)}{August 2017}
\talkvenue{University of Toronto DCS Summer Research Program}{Mid-summer research talk}{Toronto (Canada)}{July 2017}
\talktitle{Applications of Geometry Processing to Computer Graphics}
\talkvenue{University of Oviedo}{B.Sc. in Mathematics Thesis Defense}{Oviedo (Spain)}{June 2019}
\talktitle{An Introduction to Primal Inflation}
\talkvenue{University of Oviedo}{B.Sc. in Physics Thesis Defense}{Oviedo (Spain)}{June 2019}
