\mentoring{Summer Geometry Initiative}{Served as the mentor for two two-week long geometry processing research projects for eight undergraduate students.}{2023}{}
\mentoring{Graduate School Applications}{Volunteer mentoring of dozens of prospective Computer Graphics students from underrepresented groups with their graduate school application package and decisions. Successful applicant destinations include MIT, UCSD, University of Toronto, UBC and others.}{2020 - 2023}{}
\mentoring{Canada-Wide Science Fair}{Mentored grade 11 students with their project as part of University of Toronto's Pursue STEM}{Spring 2022}{}
\mentoring{Canadian Black Scientists Network Youth Science Fair}{Mentored grade 11 students with their project as part of University of Toronto's Pursue STEM}{Winter 2022}{}
\mentoring{University of Toronto DCS Graduate Applications Mentorship Program}{Mentor for several prospective graduate students.}{Fall 2021}{}
\mentoring{SIGGRAPH Graduate Applications Mentorship Program}{Mentor for several prospective graduate students.}{Fall 2021}{}
\mentoring{Creating a better summer experience: A DEI workshop}{DEI workshop for mentors of undergraduate students, organized by the Center for Minorities in the Mathematical Sciences.}{Spring 2021}{}
\mentoring{Creating a better summer experience: A DEI workshop}{DEI workshop for mentors of undergraduate students, organized by the Center for Minorities in the Mathematical Sciences.}{Spring 2021}{}
\mentoring{Fields Undergraduate Summer Research Program}{Graduate research mentor for a group of four undergraduate researchers.}{2020 - 2021}{}
